\section{Appendix}
\label{sec:appendix}
Interview instrument
\begin{enumerate}
\item What is your age, please?
\item What is your identified gender, please?
\item Can you please tell me about your professional experience with network or cybersecurity issues (training, work domains, research, etc.)?
(\item For experts) Did you have prior professional/research experience with biometrics before using them with personal devices?
\item What biometrically-enabled mobile devices do you currently use (smartphones, laptops, tablets, wearables, other)? (Describe device, how long it has been owned, unlocking method/s, how long methods have been used, interval between use of biometrics and first getting the device)
\item To what extent was security a part of this decision to use any of these devices?
\item Were any of these devices provided by an employer, or did work requirements influence your choice of device? Would you be comfortable using biometrics on a device for work?
\item Do your security settings or level of concern change in different environments? Would you want your device to modify settings for you automatically (i.e. less secure at home, versus when traveling)? 
\item What if that automatic configuration was performed by a third party, rather than the device manufacturer or your Internet provider? Would you anything about the security of that arrangement make you uncomfortable, or no?
\item For the devices you own now, why did you select these authentication methods? Did work policies influence your choice of unlocking method?
\item How did biometrics figure into your choice of personal device? How do you expect this will this change for you when selecting your next personal device?
\item Do you have any reservations about authenticating for work purposes on a personal mobile device?
\item Would you feel differently about using biometrics on a work device, compared to a personal device, or would your outlook be the same? 
\item Do you have any concerns about re-sale or compromise of your biometric data, or no? What about behavioral data collected by your device?
\item Have you ever tried to biometrically unlock a device (yours or someone else) using the wrong passcode (to test it out) or no?
\item Do you use any additional mobile security measures (such as a VPN, extra disk or message encryption, passcode changes, or strong passcodes)?
\item Which fingers, or other biometric features, do you have registered on your devices?
\item What do you remember about setting up your biometric unlocking? Did you have any problems?
\item Do you remember any notable problems or benefits that have occurred for you from using biometrics?
\item Any negative experiences for you or somebody you know with the security of your mobile devices (i.e. theft, hacking, data loss, shoulder surfing, etc.)? If so, did your unlocking behavior change as a result?
\item Which method do you think of as the primary way of unlocking the phone? Is this how the phone is designed? 
\item Do you share passcodes with anyone else (e.g. significant other, friends, family)?
\item How do you share your devices with others (phone or laptop)? How do you handle authentication in those instances?
\item Has your choice in authentication methods for your devices changed at all over time?
\item Did you try using biometrics when they became available, or did you wait? Why?
\item Do you use biometrics to control applications, apart from device unlocking? (If so, has this changed at all over time?)
\item Can you describe your view of biometrics when first tried using them? How did you try using them?
\item How do you feel about using them now? Are they adequately secure, reliable, usable?
\item Does the amount of security risk you accept vary between devices? Has this changed over time?
\item Are their situations where you think differently about your device authentications?
\item Would you be comfortable using biometrics on a device for work?
\item Can you recall an example of how you have changed your authentication behavior because of information you learned, for example, perhaps trying a new method, changing a setting, or avoiding a feature?
\item How do you develop typically develop your opinion on the trustworthiness of new technology?
\item What sources do you look at for that sort of information?
\item Do you recall what your opinion was on biometric authentication when it was first introduced widely for mobile devices? 
\item To the extent you're comfortable, can you describe your approach for storing sensitive work or personal data on your mobile devices? How has this changed over time?
\item Are you responsible for setting or advising on authentication for others (professionally or personally)? What do you tell others about using biometrics?
\item Has your opinion on the reliability of biometrics changed over time? Was this from direct experience, or some other input?
\item Do you feel the security of biometrics has improved or not from its first introduction?
\item Do you have any concerns about traveling internationally with BAM-enabled devices, or no?
\item Are you aware of any spoofing methods for BAM, or no?
\item Would you require BAM on future personal devices, or can you do without it?
\item Please recall an example of when you learned something new about biometric authentication—this could be a story you heard directly, an academic publication, or news item. (What was it about? What was the source, and medium (article, conversation, etc.)? About how long ago did you hear this information? Do you remember where you heard this? What kind of format was the information in (i.e. story, policy, advice)? Was the information positive, negative, or neutral regarding biometrics? Did you think it was true? Was the information portrayed in an intense or sensationalistic way, or not? Was the information portrayal of biometrics figurative or literal?) 
\end{enumerate}
